Computer Science House Constitution

### 2019-02-25 articles.tex
Update articles.tex

\asection{Delaying an Election}
During a House Meeting prior to the election, the Chairman may chair a fifty percent vote to postpone the election by a specified time period. See \ref{Fifty Vote}.
If the vote fails, the election must be held on normal time.

>>>>

\asection{Delaying an Election}
During a House Meeting prior to the election, the Chairman may chair a immediate fifty percent vote to postpone the election by a specified time period. See \ref{Fifty Percent}. This vote cannot take place for elections taking place for the next standard operating year's Executive Board.
If the vote fails, the election must be held on normal time.
